\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\vspace{-1em}
A patent is a set of exclusive rights granted to an inventor to protect 
their invention for a limited period of time. Patent prior art search involves 
finding previously granted patents, 
scientific articles, product descriptions or any other published work 
%scientific articles, product descriptions or any other published work that may be relevant
%or any published work, such as scientific 
%articles or product descriptions that may be relevant 
to a new patent application.
Many well-known Information Retrieval (IR) techniques, which are proven effective 
for web search such as typical query expansion methods, are unsuccessful for patent 
prior art search.
In this thesis, we mainly investigate the reasons that generic IR techniques are not 
effective for prior art search on the CLEF-IP test collection.   
%Hence in this thesis, we analysed the reasons lead in low effectiveness 
%of general IR techniques for prior art search on the CLEF-IP test collection. 
First, we analyse the errors caused due to data curation and experimental settings 
like applying International Patent Classification codes assigned to the patent topics 
to filter the search results.  
Then, we investigate the influence of term selection on retrieval
performance on the CLEF-IP prior art test collection, starting with
the Description section of the reference patent and using Language Models (LM) and BM25
scoring functions. We find that an oracular relevance feedback system,
which extracts terms from the judged relevant documents far
outperforms the baseline and performs twice as well on Mean Average Precision (MAP) as the best
competitor in CLEF-IP 2010. We find a very clear term selection value
threshold for use when choosing terms.  We also noticed that most of
the useful feedback terms are actually present in the original query
and hypothesise that the baseline system could be substantially
improved by removing negative query terms.
%Furthermore, a similar oracular query restricted
%to select terms from only the reference patent performs nearly as well
%as unrestricted term selection suggesting that query reduction methods
%should suffice for state-of-the-art performance on CLEF-IP 2010.
We tried four simple automated approaches to identify negative terms
for query reduction but we were unable to improve on the baseline
performance with any of them. However, we show that a
simple, minimal feedback interactive approach where terms are selected
from only the first retrieved relevant document outperforms the best
result from CLEF-IP 2010, suggesting the promise of interactive methods
for term selection in patent prior art search.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 