%Query or topic is the the request for information in any retrieval system. An effective query can lead in retrieving the required information. Queries formulated by users are not usually optimal for retrieval process, therefore, they need to be transformed by techniques such as query expansion or query reduction. 
The patent prior-art search scenario begins with the full patent application as a query. A full text as a query is a challenge compared to a classical IR, since it is not focused on the information that the user needs. In order to achieve good retrieval results, it is important to extract the best representative text with the proper weights. Therefore, query generation based on query document is essential to reduce the difficulty of formulating effective queries by users. 
%The query created before the retrieval can be modified or enhanced after retrieval. In this section, the initial query formulation will be discussed and in the next section, post-retrieval query reformulation will be covered. 
\paragraph{Terms Selection}
\ \\
\input{background/term_select}

\paragraph{Using Phrases instead of Terms}
\ \\
Most of query formulation techniques rely on terms, but encouraging results have been obtained using phrases recently~\citep{becks2010phrases}. Early results demonstrated that an NLP-based grouping of terms can increase the performance compared to the bag-of-words approach, though the increase is smaller than in a non-patent collection~\citep{osborn1997evaluating}. Another task could improve retrieval effectiveness by adding syntactic phrases in the form of dependency triples, to a bag-of-words representation~\citep{d2011combining}. Key Phrase Extraction (KPE) algorithms is another way to form a query based on phrases. A list of phrases, generated by a KPE algorithm, can succinctly represent a complex and lengthy patent. ~\citep{verma2011applying}.

\paragraph{Diverse Query Generation}
\ \\
In this approach, the focus is on generating diverse queries that can improve overall retrieval effectiveness in sessions rather than generating a single best query that can retrieve more relevant documents from a single retrieval result (i.e., more relevant documents in aggregated retrieval results obtained by multiple queries in a session). Diverse query generation is important because query documents typically contain several different aspects (or topics) and different types of relevant documents may be related to these aspects. To identify aspects, 500 top terms based on their tf-idf rank, are clustered into $ n $ sets with respect to their similarity. Each distinct sets of terms represents one query aspect, then top $ k $ retrieved documents for each sub-query consider as pseudo-relevant documents (PRD) and those ranked below the top $ k $ are non-relevant documents (NRD). Then the query is generated by decision tree. ~\citep{kim2014searching, kim2014diversifying}.