\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\vspace{-1em}
A patent is a set of exclusive rights granted to an inventor to protect their invention for a limited period of time. Patent prior art search involves finding previously granted patents, or any published work, such as scientific articles or product descriptions that may be relevant to a new patent application.
In this research, we investigate the influence of term selection on retrieval
performance on the CLEF-IP Prior Art test collection, starting with
the Description section of the reference patent and using LM and BM25
scoring functions. We find that an oracular relevance feedback system,
which extracts terms from the judged relevant documents far
outperforms the baseline and performs twice as well on MAP as the best
competitor in CLEF-IP 2010.  We find a very clear term selection value
threshold for use when choosing terms.  We also noticed that most of
the useful feedback terms are actually present in the original query
and hypothesized that the baseline system could be substantially
improved by removing negative query terms.
%Furthermore, a similar oracular query restricted
%to select terms from only the reference patent performs nearly as well
%as unrestricted term selection suggesting that query reduction methods
%should suffice for state-of-the-art performance on CLEF-IP 2010.
We tried four simple automated approaches to identify negative terms
for query reduction but we were unable to improve on the baseline
performance with any of them.  However, we show that a
simple, minimal feedback interactive approach where terms are selected
from only the first retrieved relevant document outperforms the best
result from CLEF-IP 2010 suggesting the promise of interactive methods
for term selection in patent prior art search.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 