\chapter*{Declaration}
\addcontentsline{toc}{chapter}{Abstract}
\vspace{-1em}
I hereby declare that this thesis is my original work that has been done in 
collaboration with other researchers and me as the main author. This document has
not been submitted for any other degree or award in any other university or educational 
institution. 
Certain aspects of these contributions have been published in 
collaboration with other researchers as follows:
%Chapter~\ref{cha:analysis} of this thesis has been published in collaboration to other
%researchers to the 38th annual ACM SIGIR conference:
%~\citep{mona2015termselection}
\begin{itemize}
\bibitem[{Golestan~Far et~al.(2015)Golestan~Far, Sanner, Bouadjenek, Ferraro,
  and Hawking}]{mona2015termselection}
\textsc{Golestan~Far, M.; Sanner, S.; Bouadjenek, R.; Ferraro, G.; and Hawking,
  D.}, 2015.
\newblock On term selection techniques for patent prior art search.
\newblock In \emph{Proceedings of the 38th International ACM SIGIR Conference
  on Research and Development in Information Retrieval}, SIGIR '15 (Santiago,
  Chile, August 09 - 13 2015). ACM, New York, NY, USA.
  
%\bibitem[{Golestan~Far et~al.(2015)Golestan~Far, Sanner, Bouadjenek, Ferraro,
%  and Hawking}]{mona2015termselection}
%\textsc{Golestan~Far, M.; Sanner, S.; Bouadjenek, R.; Ferraro, G.; and Hawking,
%  D.}, 2015.
%\newblock On term selection techniques for patent prior art search.
%\newblock In \emph{Proceedings of the 38th International ACM-SIGIR Conference
%  on Research and Development in Information Retrieval} (Santiago, Chile,
%  August 09 - 13 2015). ACM.
\end{itemize}
I developed my baseline system based on Reda\footnote{Reda has been working on patent prior art search for three months as a visitor at NICTA before I start. He published his work in~\citep{Bouadjenek:2015:SQR:2746090.2746092}} Bouadjenek's baseline 
to investigate the reasons that his experiments on different query reformulation 
techniques ended in only little improvement over the baseline. The results of my analysis ended in proposing interactive methods as a promising avenue for simple but highly effective term selection in prior art search.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 