% Reda: please have a look at this section and consider revising
%       as appropriate.  -Scott


Our work is different from pioneer studies on patent retrieval, as we
closely looked into the problem rather than solutions to figure out
the causes that generic IR models which are based on term matching
process, do not work efficiently in patent domain. However, we cite here few works that focus mainly on query reformulation for patent search. 
In \cite{Itoh2003}, authors proposed a new term selection method using different term
frequencies depending on the genre in the NTCIR-3 Patent Retrieval Task.
Xue and Croft \cite{xue2009transforming} conducted a series of experiments
in order to examine the effect of different patent fields, and concludes
with the observation that the best MAP is
achieved using the text from the description section. Also, Fuji \cite{Fujii2007}
showed that retrieval effectiveness can be improved by combining IR
methods with the result of citation extraction.
Bashir et al. \cite{Bashir2010} propose query expansion with pseudo-relevance
feedback. Terms are selected using a using a machine
learning approach, by picking terms that may have a potential positive
impact on the retrieval effectiveness. Verma and Varma
\cite{Verma2011} propose a different approach, which instead of using
the patent text to query, use its IPC codes, which are expanded using the citation network. The formed
query is used to perform an initial search. The results are then re-ranked
using queries constructed from patent text.
Magdy et al.~\cite{magdy2011study} studied works on query expansion in patent
retrieval and discussed that standard query expansion techniques are
less effective, where the initial query is the full texts of query
patents. Mahdabi et al.~\cite{Mahdabi2013} used term proximity
information to identify expansion terms. Ganguly et
al.~\cite{ganguly2011patent} adapted pseudo relevance feedback for
query reduction by decomposing a patent application into constituent
text segments and computing the Language Modelling (LM) similarities
of each segment from the top ranked documents. The least similar
segments to the pseudo-relevant documents removed from the query,
hypothesizing it can increase the precision of retrieval. Kim et
al.~\cite{kim2014diversifying} provided diverse query suggestion using
aspect identification from a patent query to increase the chance of
retrieving relevant documents. Mahdabi et al.~\cite{mahdabi2014patent}
used linked-based structure of the citation graph together with IPC
classification to improve the initial patent query. 
Finally, other works investigated query suggestion for patent prior
art search, which reflect real-life scenario of examiners, who form
reproducible boolean queries \cite{Adams2011,Azzopardi2010,Kim2011}.

